An Evolutionary Algorithm for the Multiobjective Risk-Equity Constrained Routing Problem

### 2011-11-30 DAW_hazmatHypE/trunk/paper/hazmatRouting_EvolOptim.tex
added description of Sec. 4.2 about the differences between the instances (including new plot)

\TODO{show results and talk about them}

>>>>

Figure~\ref{fig:compareAll} shows the non-dominated solutions of 10 independent HypE runs for each instance. What can be observed are three main statements. First of all, cost and risks of the found non-dominated solutions are highly correlated, as they are for each single arc in the problem formulations; therefore, the problem is not truly three-objective but rather bi-objective. Secondly, the range of the objective function values for the found non-dominated solutions follow the number of trucks in the problem instance, i.e., the more trucks a problem instance has the more costs, total and equity risk can be expected in the solutions found. However and thirdly, this relationship is not linear in the plots of Fig.~\ref{fig:compareAll} as can be seen, for example, between the lazio\_4\_2 and the lazio\_4\_3 instance. Though the number of trucks per commodity differs by a factor of 3 between them, the objective function values of the resulting non-dominated solutions after 1,000 generations are slightly further away. The reason for that is the much smaller search space for the lazio\_4\_3 instance which can be searched more exhaustively by the algorithm with the same number of function evalutions---resulting in a better convergence towards the Pareto front.

\begin{figure}
	\centering
	\includegraphics[width=0.75\columnwidth]{../experiments/randVsCost/compAll_2000gens.eps}
	\caption{\label{fig:compareAll} Comparison between the different instances lazio\_2 (squares), lazio\_3 (circles), lazio\_4\_1 (diamonds), lazio\_4\_2 (crosses), and lazio\_4\_3 (stars). Shown are the non-dominated solutions in the final populations of 10 independent HypE runs with population size 50 after 2000 generations.}
\end{figure}
